MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
Added threat model

\section{Threat Model}
TODO

>>>>

\section{Threat Model}
In our threat model we are assuming the attack will be carried out in a public place where the attacker
can get within 30-100 feet of the victim. A couple examples include places like an airport, an office building, or a coffee shop. In any of these places it would be extremely easy for an attacker to get nearby the victim without appearing suspicious.

The victim of the attack is someone who is using a Bluetooth keyboard to type on any device. The devices could include a tablet, laptop, or PC. The victim would eventually in the course of their activities type some sensitive information. This could include payment information, passwords, or some other financial information.

The person performing the attack will most likely be using a laptop. They may or may not have specialty sniffing hardware. Their main goal will be attempting to log passwords or financial information like credit card numbers. To perform their attack they would most likely sit inconspicuously nearby the victim or hide out in a van outside the public place the attack is being carried out at.
